---
title: "Homework 8"
author: "Elijah Wang"
date: "2025-04-11"
output: pdf_document
---
github link: https://github.com/ReagentRock/Homework8.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mosaic)

creatine<-read.csv("creatinine.csv")
covid<-read.csv("covid.csv")
milk<-read.csv("milk.csv")

```

## Problem 1: regression warm up


```{r,include=FALSE}
creatineModel<-lm(creatclear~age,data=creatine)
```

A) For a 55-year old, we would expect a clearance rate of 113.724ml/minute. We determined this by creating a linear regression of creatinine clearance rate to age to get the rate by following equation:
y=147.8129-0.6198x
when x=55 then y equals 113.7239.

B)
Creatinine clearance rate decreases at a rate of -0.6198ml/minute per year. I found this number by fitting a linear regression of the creatinine clearance rate and age whereas the slope(or beta1) is that creatinine clearance rate per year. 


C)
a 40 year old averages a creatinine clearance rate of(y=147.8129-0.6198(40)) 123.0209
The 60 year old, however, averages a creatinine clearance rate of (y=147.8129-0.6198(60)) 110.6249.
Looking at the residuals the 40 yr differed by 11.971(135-123.029)
while the 60 yr differed by 1.3751(112-110.6249)
As such, the 40 year old is healthier due to having a higher creatinine clearance rate relative to their age compared to that 60 year old.

## Problem 2: Modelling disease growth

```{r pressure, echo=FALSE,include=FALSE}
covidModelI<-lm(log(deaths[country=="Italy"])~days_since_first_death[country=="Italy"],data=covid)
covidModelS<-lm(lm(log(deaths[country=="Spain"])~days_since_first_death[country=="Spain"],data=covid))

covidModelI_B<-do(10000)*lm(log(deaths[country=="Italy"])~days_since_first_death[country=="Italy"],data=resample(covid))
confint(covidModelI_B)

covidModelS_B<-do(10000)*lm(lm(log(deaths[country=="Spain"])~days_since_first_death[country=="Spain"],data=resample(covid)))

confint(covidModelI_B)
confint(covidModelS_B)
```
1. Italy has an estimated growth rate of 18.346% with a 95% confidence interval of %15.907 to %20.784 . As such, the doubling time has a 95% confidence interval of 3.4 to 4.4 days and an estimate of 3.9 days.

2. Spain has an estimated growth rate of 27.586% with a 95% confidence interval of 23.344% to 31.828%. As such, the doubling time has a 95% confidence interval of 2.2 to 3.0 days and an estimate of 2.6 days.

3. The line plot:
```{r}
ggplot(covid)+geom_line(aes(x=days_since_first_death,y=deaths,colour = country))+xlab("Time(days)")+ylab("Reported COVID Deaths(people)")+ggtitle("Reported COVID Deaths Over Time")

```

## Problem 3: Price elasticity and demand

```{r,include=FALSE}
milkModel<-lm(log(sales)~log(price),data=milk)

milkModel_B<-do(10000)*lm(log(sales)~log(price),data=resample(milk))
confint(milkModel_B)
```
The estimate 95% confidence interval for price elasticity for milk is -1.772 to -1.450. By this interval we can estimate the price elasticity is -1.619. I obtained this value by creating a power model using the lm function on the log of the two variables respectively. I then simulated this model 100,000 times and took the confidence interval of that bootstrapped model.
